### 2019-04-08 ms/apendice1.Rmd
add apéndice

---
title: ""

output:
  word_document:
    fig_caption: yes
    fig_height: 6
    fig_width: 7.5
    highlight: null
    reference_docx: Ecosistemas_template.docx
csl: ecosistemas.csl
bibliography: 
  - appendix.bib
nocite: '@*'
editor_options: 
  chunk_output_type: console
---

**Apéndice 1. Publicaciones que han utilizado el Inventario Forestal Sinfonevada antes de su integración en un repositorio.**

**Appendix 1. Publications that have used the Sinfonevada Forest Inventory before its integration into a repository.**